### 2019-08-23 report/MSc_Report.tex
corrections

\begin{align}
\theta &= m_t - m_c & \se_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}
\end{align}

Cohen's $d$ and its standard error $\se_d$ can similarly be obtained by

\begin{align}
d &= \frac{m_t - m_c}{\se} \label{eq:hedges.g} & \se_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}
\end{align}

Both estimators take into account that the two groups might have unequal variances. \\ 
A  $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test. The $t$ statistic is obtained, using $\se_d$ and $d$ from \eqref{eq:hedges.g}, by

\begin{align}
t &= d/(\se_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
\end{align}
and the  $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:

\begin{align}
p &= 2(1-F(\abs{t})) \nonumber
\end{align}

@@

\begin{align}
\hat{\theta} &= \log\bigg[\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}\bigg] \nonumber \\
\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c) \nonumber
\end{align}

@@

\begin{align}
\hat{\theta} &= \log\bigg(\frac{e_t/n_t}{e_c/n_c}\bigg) \label{eq:risk.ratio} \\
\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c \label{eq:risk.ratio.variance}
\end{align}

@@

\begin{align}
\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i}. \label{eq:fixed.effects}
\end{align}
This estimator minimizes the variance between the effects. An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$. The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.\\
The random effects model \citep{whitehead} assumes instead that 
\begin{align}
\theta_i \sim N(\mu_i, \se_i^2) &&
\mu_i \sim N(\theta_M, \tau^2) \label{eq:random.effects} 
\end{align}

@@

\begin{align}
\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2) \nonumber %\label{eq:random.effects.marginal}
\end{align}

@@

\begin{align}
Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg] \label{eq:Tau.definition}
\end{align}

@@

\begin{align}
w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1 \nonumber
\end{align}

@@

\begin{align}
\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1 \label{eq:paulemandel}
\end{align}

@@

\begin{align}
F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1) \nonumber
\end{align}

@@

\begin{align}
y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:simple.regression}
\end{align}
$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution. We look for the solution that minimizes the squared residuals, the least-squares solution. Formally,

\begin{align}
\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big) \label{eq:least.squares}
\end{align}

@@

\begin{align}
\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
\end{align}

Is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals. Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$. The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are

\begin{align}
\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1} \label{eq:regression.variances}
\end{align}

@@

\begin{align}
% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x} \nonumber
\end{align}

@@

\begin{align}
\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)\Big) \nonumber
\end{align}

with the positive weights $w_i$ penalizing large squared residuals for some $i$ more if $w_i$ is larger. \\
Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals. The estimates in \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} can again be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$. \label{weighted.regression} \\
The introduction of group-specific random effects allows to analyze grouped or repeated measurements by linear regression. Let $j$ be the group index, $i$ the index of the single observation from the group $j$ and $x_i$ the $i^\textrm{th}$ row of $\mathbf{X}$, $(1, \mathbf{X}_{i2})$. Then the equation

\begin{align}
\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i} \label{eq:one.random.intercept}
\end{align}

gives the marginal distribution of $\mathbf{y}_i$ depending on $U{_j}$ and $\epsilon_i$. The random effects $U_j \sim N(0, \mathbf{G})$ and the residual error term $\epsilon_i \sim N(0, \tau^{2})$ are independent from each other. Let $\mathbf{y}_j$ be a vector of all observations of group $j$. The expectation $\mathbb{E}(\mathbf{y}_i)$ is still $x_i \beta$, but the covariance between the observations within a group $j$, is modeled as

\begin{align}
\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j} \label{eq:random.intercepts.covariance}
\end{align}

where $\D_j$ is in the case of the random intercept model a $n_j \times 1$ matrix of 1's, $\mathbf{G}$ is a scalar to be estimated and $\mathbf{I}_{n_j}$ is an $n_j \times n_j$ identity matrix. Thus, if $\mathbf{G} \neq 0$, the observations within a group will be uniformly correlated (uniform correlation between each observation). \\
Nested groups can be modeled by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
An extension of the random intercepts model is the random slopes model, which allows for additional, group-specific slopes with respect to a explanatory variable $x$. It can be implemented by modifying \eqref{eq:one.random.intercept}. Let $\mathbf{U}_j$ be a two-dimensional random vector with a $2 \times 2$ covariance matrix $\mathbf{G}$. Again, we can specify the marginal distribution of a observation $i$ within a group $j$:

\begin{align}
\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i \label{eq:one.random.intercept.and.slope}
\end{align}

@@

\begin{align}
\hat{\mathbf{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
\end{align}

with $m$ being the number of groups and $\hat{\mathbf{V}}_j$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_j$ is distributed as

\begin{align}
\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j).
\end{align}
The matrices $\sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j$ and $\hat{\mathbf{V}}_j$ are assumed to be positive definite  . The approximate covariance matrix of $\hat{\beta}$ is given by

\begin{align}
\hat{\Cov}(\hat{\beta}) &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1}
\end{align}

@@

\begin{align}
\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2} \label{eq:begg.stand.var} 
\end{align}

@@

\begin{align}
Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18} \nonumber
\end{align}

Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$. A two-sided  $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
\begin{align}
p &= 2\cdot(1-\Phi(\abs{Z})) \nonumber
\end{align}

@@

\begin{align}
\theta/\se &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2) \label{eq:radial.plot} 
\end{align}

@@

\begin{align}
\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-2}\sigma^2) \label{eq:egger.plot}
\end{align}

with weights $w = 1/\se^2$. Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent. The corresponding  $p$\hspace{0.4mm}-value is then used as evidence for a small study effect. Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.

@@

\begin{align}
\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2) \label{t.sharp.regression}
\end{align}

@@

\begin{align}
\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \nonumber \\
 \se^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)} \nonumber
\end{align}

@@

\subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
\citealp{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable. When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution. Using the Mantel-Haenszel log odds ratio and the marginal total parameters, the variance and the expectation of $E_t$ is calculated. The inverse of the variance $\se(E_t)^2$ and the standardized event count

\begin{align}
(e_t - \mathbb{E}(E_t))/\se_i
\end{align}

are then used as before in Begg and Mazumdar's test.

@@

\begin{align}
\theta_i &= \arcsin{(e_t/n_t)} - \arcsin{(e_c/n_c)} \nonumber &
\se_i^2 &= 1/(4n_t) + 1/(4n_c) \nonumber
\end{align}

@@

\subsection{Excess Significance Test} \label{sec:excess.significance}
Publication bias does not need to be accompanied by small study effects. In the absence of any treatment effect, significant effects could be included in a meta-analysis on both directions of treatment effects (\ie large \textit{and} small effects) are published. Also, the afore-mentioned methods do not use statistical significance directly to investigate publication bias. Thus, a different test is introduced. \\
\citealp{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
%Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects meta-Analysis \eqref{eq:fixed.effects}. Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold. Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to be accepting a true result. Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$. The power of study $i$ can be estimated as:

\begin{align}
1 - \hat{\beta}_i &= F(z_\alpha) 
\end{align}

with $F$ being the cumulative normal distribution with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just

\begin{align}
E &= \sum_{i = 1}^n (1 - \beta_i) \nonumber
\end{align}

@@

\begin{align}
\chi  &= \bigg( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\bigg) \nonumber
\end{align}

and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom. Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small. We will get a one sided $p$\hspace{0.4mm}~-value for excess significance, $\P(X \geq O)$, by computing

\begin{align}
p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big) \nonumber
\end{align}

with $p = E/n$ and $X$ being a binomial random variable with probability $p$.

@@

\begin{align}
\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \label{eq:limitmeta.regression} \\
\epsilon_i &\stackrel{\textrm{iid}}{\sim} N(0,1)
\end{align}

@@

\begin{align}
\mathbb{E}\big((\theta_i - \beta_0)/\sqrt{\se_i^2}\big) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
\mathbb{E}(\theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0 \nonumber
\end{align}

@@

\begin{align}
\theta_i &\sim N(\mu_i, \sigma_i^2) &
\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
\end{align}
which is identical to the random-effects meta-analysis setting. $\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance. This is termed the \textit{population model}. \\
The \textit{selection model} is defined as follows. Suppose a selection of studies with reported %($\neq$ estimated) 
standard errors $\se$ (possibly different from $\sigma$). Only a proportion of the selection will be published, with the parameter $a$ defining the overall proportion of published studies and $b$ (assumed to be positive) defining how fast this proportion increases with $\se$ becoming smaller. Formally, the probability of selection given a reported standard error $\se$ is defined as

\begin{align}
P(\textrm{select}\given \se) &= \Phi(a + b/\se) \nonumber %\label{copas.selection1}
\end{align}

@@

\begin{align}
z = a + b/\se + \delta \nonumber %\label{copas.selection2}
\end{align}

with $\delta \sim N(0,1)$. $z$ is interpreted as the \textit{propensity for selection}. It is defined that the sign of $z$ must be positive in order for the study to be selected.
$a$ is some kind of global selection rate for each study and $b$ decides about the decline of selection probability with increasing $\se$.\\
So far, we have, for a study $i$

\begin{align}
\theta_i = \mu_i + \sigma_i\epsilon_i \nonumber \\ 
\mu_i \sim N(\theta, \tau^2) \nonumber \\
z_i = a + b/\se_i + \delta_i \nonumber
\end{align}

>>>>

\begin{align}
\theta &= m_t - m_c & \textrm{sd}_\theta &= \sqrt{\textrm{sd}_t^2/n_t + \textrm{sd}_c^2/n_c}.
\end{align}

Cohen's $d$ and its standard error $\textrm{sd}_d$ can similarly be obtained by

\begin{align}
d &= \frac{m_t - m_c}{\textrm{sd}_\theta} & 
\textrm{sd}_d &= \sqrt{\frac{(n_t - 1)\textrm{sd}_t^2 + (n_c - 1)\textrm{sd}_c^2}{n_t + n_c - 2}}. \label{eq:cohensd}
\end{align}

Both estimators take into account that the two groups might have unequal variances. \\ 
A  $p$\hspace{0.4mm}-value to test the null hypothesis that the mean between group is equal is commonly obtained with the Students $t$-test. The $t$ statistic is obtained, using $\textrm{sd}_d$ and $d$ from \eqref{eq:cohensd}, by

\begin{align}
t &= d/(\textrm{sd}_d\sqrt{(1/n_t)+(1/n_c)}) \nonumber
\end{align}
and the  $p$\hspace{0.4mm}-value can be obtained with the cumulative Student's $t$-distribution $F$ with $n_t + n_c - 2$ degrees of freedom:

\begin{align}
p &= 2(1-F(\abs{t})). \nonumber
\end{align}

@@

\begin{align}
\hat{\theta} &= \log\bigg[\frac{e_t\cdot(n_c - e_c)}{e_c\cdot(n_t - e_t)}\bigg] \nonumber \\
\hat{\se}^2 &= 1/e_t + 1/(n_t - e_t) + 1/e_c + 1/(n_c - e_c). \nonumber
\end{align}

@@

\begin{align}
\hat{\theta} &= \log\bigg(\frac{e_t/n_t}{e_c/n_c}\bigg) \label{eq:risk.ratio} \\
\se^2&= 1/e_t - 1/n_t + 1/e_c - 1/n_c. \label{eq:risk.ratio.variance}
\end{align}

@@

\begin{align}
\theta_M &= \frac{\sum_{i = 1}^n w_i \theta_i}{\sum_{i = 1}^n w_i} &
\se_M^2 &= \frac{1}{\sum_{i = 1}^n w_i}. \label{eq:fixed.effects}
\end{align}

This estimator minimizes the variance between the effects. An estimate $\hat{\theta}_M$ can be obtained by plugging in the observed treatment effects and variances $\hat{\theta}_i$ and $\hat{\se}_i^2$. The underlying idea is that we assume $\theta_i \sim N(\theta_M, \se_i^2)$, $\theta_M$ being the true effect, all $\theta_i$ being distributed around an equal mean.\\
The random effects model \citep{whitehead} assumes instead that 
\begin{align}
\theta_i \sim N(\mu_i, \se_i^2) &&
\mu_i \sim N(\theta_M, \tau^2). \label{eq:random.effects} 
\end{align}

@@

\begin{align}
\theta_i \given \mu_i \sim N(\theta_M, \se_i^2 + \tau^2). \nonumber %\label{eq:random.effects.marginal}
\end{align}

@@

\begin{align}
Q &= \sum_{i = 1}^n w_i(y_i - \theta_M)^2 & C &= \sum_{i = 1}^n w_i - \frac{\sum_{i = 1}^n w_i^2}{\sum_{i = 1}^n w_i} \label{eq:Q.heterogeneity} \\
\tau^2 &= \max\bigg[0, \frac{Q - (n-1)}{C}\bigg]. \label{eq:Tau.definition}
\end{align}

@@

\begin{align}
w_i \textrm{Var}(\theta_i) &= 1 & \textrm{Var}(\sqrt{w_i}\theta_i) = 1. \nonumber
\end{align}

@@

\begin{align}
\se^2(w_i\theta_i) &= \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} & \frac{\sum_{i = 1}^n w_i(\theta_i - \theta_M)^2}{n-1} = 1. \label{eq:paulemandel}
\end{align}

@@

\begin{align}
F(\tau^2) &= \sum_{i = 1}^n w_i(\theta_i - \theta_M)^2 - (n-1). \nonumber
\end{align}

@@

\begin{align}
y &= \beta_0 + \beta_1 x + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:simple.regression}
\end{align}

$\epsilon$ is the residual noise term that becomes necessary when $n$ pairs $(x_i, y_i)$ are given and there is no exact solution. We look for the solution that minimizes the squared residuals, the least-squares solution. Formally, we write:

\begin{align}
\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n y_i - \beta_0 - \beta_1 x_i\Big). \label{eq:least.squares}
\end{align}

@@

\begin{align}
\hat{\mathbf{\beta}} &= (\mathbf{X}^\top \mathbf{X})^{-1} \mathbf{X}^\top \mathbf{y} \label{eq:regression.parameters}
\end{align}
is an estimator of $\mathbf{\beta}$ that minimizes the squared residuals. Let $\hat{\mathbf{y}} = \mathbf{X}\hat{\mathbf{\beta}}$ and $\hat{\mathbf{r}} = \hat{\mathbf{y}} - \mathbf{y}$. The variance estimates $\hat{\sigma}^2$ and $\hat{\mathbf{s}}_\beta^2$ are

\begin{align}
\hat{\sigma}^2 &= \frac{1}{n-2}\mathbf{r}^\top \hat{\mathbf{r}} & \hat{\mathbf{s}}_\beta^2 &= \hat{\sigma}^2 (\mathbf{X}^\top \mathbf{X})^{-1}. \label{eq:regression.variances}
\end{align}

@@

\begin{align}
% \hat{\beta_1} &= \frac{\sum_{i = 1}^n (x_i - \bar{x})(y_i - \bar{y})}{\sum_{i = 1}^n (x_i - \bar{x})^2} &
\hat{\beta}_0 &= \bar{y} - \hat{\beta}_1 \bar{x}. \nonumber
\end{align}

@@

\begin{align}
\operatorname*{argmin}_{\beta_0, \beta_1}\Big(\sum_{i = 1}^n w_i(y_i - \beta_0 - \beta_1 x_i)\Big) \nonumber
\end{align}
with the positive weights $w_i$ penalizing large squared residuals for some $i$ more if $w_i$ is larger. \\
Let $\mathbf{W}$ be a $n \times n$ matrix with $\mathbf{W}_{ii} = w_i$, the weights on the diagonal and zeros on the off-diagonals. The estimates in \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} can again be used if $\mathbf{X}$ is exchanged with $\mathbf{X}^\star =  \mathbf{W} \mathbf{X}$ and $\mathbf{y}$ with $\mathbf{y}^\star = \mathbf{W} \mathbf{y}$. \label{weighted.regression} \\
The introduction of group-specific random effects allows to analyze grouped or repeated measurements by linear regression. Let $j$ be the group index, $i$ the index of the single observation from the group $j$ and $x_i$ the $i^\textrm{th}$ row of $\mathbf{X}$, $(1, \mathbf{X}_{i2})$. Then the equation

\begin{align}
\mathbf{y}_i \given U_j,\epsilon_{i} =  x_i\beta + U_j + \epsilon_{i}. \label{eq:one.random.intercept}
\end{align}
gives the marginal distribution of $\mathbf{y}_i$ depending on $U{_j}$ and $\epsilon_i$. The random effects $U_j \sim N(0, \mathbf{G})$ and the residual error term $\epsilon_i \sim N(0, \tau^{2})$ are independent from each other. Let $\mathbf{y}_j$ be a vector of all observations of group $j$. The expectation $\mathbb{E}(\mathbf{y}_i)$ is still $x_i \beta$, but the covariance between the observations within a group $j$, is modeled as

\begin{align}
\Cov(\mathbf{y}_j) &= \mathbf{D}_j \mathbf{G} \mathbf{D}_j^\top + \tau^2 \mathbf{I}_{n_j}. \label{eq:random.intercepts.covariance}
\end{align}
where $\D_j$ is in the case of the random intercept model a $n_j \times 1$ matrix of 1's, $\mathbf{G}$ is a scalar to be estimated and $\mathbf{I}_{n_j}$ is an $n_j \times n_j$ identity matrix. Thus, if $\mathbf{G} \neq 0$, the observations within a group will be uniformly correlated (uniform correlation between each observation). \\
Nested groups can be modeled by extending the design matrix $\mathbf{X}$ with an additional column of 1's and using according indices that specify the nesting structure.\\
An extension of the random intercepts model is the random slopes model, which allows for additional, group-specific slopes with respect to a explanatory variable $x$. It can be implemented by modifying \eqref{eq:one.random.intercept}. Let $\mathbf{U}_j$ be a two-dimensional random vector with a $2 \times 2$ covariance matrix $\mathbf{G}$. Again, we can specify the marginal distribution of a observation $i$ within a group $j$:

\begin{align}
\mathbf{y}_i \given U_j,\epsilon_i =  x_i\beta + x_i \mathbf{U}_j + \epsilon_i. \label{eq:one.random.intercept.and.slope}
\end{align}

@@

\begin{align}
\hat{\mathbf{\beta}} &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1} \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{y}_j
\end{align}
with $m$ being the number of groups and $\hat{\mathbf{V}}_j$ being the estimated covariance, obtained by maximizing the log likelihood of the normal distribution, as $\mathbf{y}_j$ is distributed as

\begin{align}
\mathbf{y}_j \sim N(\mathbf{x}_j \mathbf{\beta}, \mathbf{V}_j). \nonumber
\end{align}

The matrices $\sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j$ and $\hat{\mathbf{V}}_j$ are assumed to be positive definite  . The approximate covariance matrix of $\hat{\beta}$ is given by

\begin{align}
\hat{\Cov}(\hat{\beta}) &= \Big( \sum_{j = 1}^m \mathbf{x}_j^\top \hat{\mathbf{V}}_j^{-1} \mathbf{x}_j \Big)^{-1}. \nonumber
\end{align}

@@

\begin{align}
\theta_i^\star &= (\theta_i - \theta_M)/\se_i^{2\star} \label{eq:begg.stand.eff}  \\
\se_i^{2\star} &= \se_i^2 - 1/\sum_{i = 1}^n\frac{1}{\se_i^2}. \label{eq:begg.stand.var} 
\end{align}

@@

\begin{align}
Z &= (u - l)/\sqrt{n(n-1)(2n + 5)/18}. \nonumber
\end{align}

Thus, large number of concordant pairs will reflect in large $\hat{u}$ and small $\hat{l}$ and thus lead to a large $\hat{Z}$. A two-sided  $p$\hspace{0.4mm}-value is obtained using the standard normal distribution $\Phi$:
\begin{align}
p &= 2\cdot(1-\Phi(\abs{Z})). \nonumber
\end{align}

@@

\begin{align}
\theta/\se &= \beta_0 + \beta_1/\se + \epsilon, & \epsilon \sim N(0, \sigma^2). \label{eq:radial.plot} 
\end{align}

@@

\begin{align}
\theta &= \beta_0 + \beta_1 \se + \epsilon, & \epsilon \sim N(0, w^{-2}\sigma^2) \label{eq:egger.plot}
\end{align}
with weights $w = 1/\se^2$. Thus testing $\beta_0$ of \eqref{eq:radial.plot} or $\beta_1$ of \eqref{eq:egger.plot} is equivalent. The corresponding  $p$\hspace{0.4mm}-value is then used as evidence for a small study effect. Plugging in  $\theta_i/\se_i, 1/\se_i$ as $y_i, x_i$ into equations \eqref{eq:regression.parameters} and \eqref{eq:regression.variances} will give the estimates for $\hat{\beta}_0, \hat{\beta}_1,\hat{\se}_{\beta_0}$ and $\hat{\se}_{\beta_1}$.

@@

\begin{align}
\theta_i \sim N(\beta_0 + \beta_1 \se_i, \se_i^2 + \tau^2). \label{t.sharp.regression}
\end{align}

@@

\begin{align}
\varphi &= e_t - (e_t - e_c)(e_t + (n_t - e_t))/(n_t + n_c) \nonumber \\
 \se^2 &= \frac{(e_t + e_c)(e_t + (n_t - e_t))(e_c + (n_c - e_c))((n_t - e_t) + (n_c - e_c))}{(n_t + n_c)^2(n_t + n_c - 1)}. \nonumber
\end{align}

@@

\subsection{Schwarzer's Test: Rank Correlation Test} \label{sec:Schwarzer}
\citet{Schwarzer} developed a test for the correlation between the event counts in the treatment group and the expected event counts $E_t - \mathbb{E}(E_t)$, where $E_t$ is a random variable. When the marginals in a two-by-two table and the log odds ratio are fixed, it can be shown that $E_t$ follows a non-central hypergeometric distribution. Using the Mantel-Haenszel log odds ratio and the marginal total parameters, the variance and the expectation of $E_t$ is calculated. The inverse of the variance $\se(E_t)^2$ and the standardized event count

\begin{align}
(e_t - \mathbb{E}(E_t))/\se_i
\end{align}
are then used as before in Begg and Mazumdar's test.

@@

\begin{align}
\theta_i &= \arcsin{(e_t/n_t)} - \arcsin{(e_c/n_c)} \nonumber &
\se_i^2 &= 1/(4n_t) + 1/(4n_c). \nonumber
\end{align}

@@

\subsection{Excess Significance Test} \label{sec:excess.significance}
Publication bias does not need to be accompanied by small study effects. In the absence of any treatment effect, significant effects could be included in a meta-analysis on both directions of treatment effects (\ie large \textit{and} small effects) are published. Also, the afore-mentioned methods do not use statistical significance directly to investigate publication bias. Thus, a different test is introduced. \\
\citet{excess.significance} developed an exploratory test to detect if the proportion of significant findings is larger than expected. 
%Note that significance is here defined as one-sided significance, with the direction of the test being the same for each study. \\
We assume that the effects are equally distributed around a true mean effect $\theta_M$, which can be estimated by fixed effects meta-Analysis \eqref{eq:fixed.effects}. Let $O$ be the number of significant study results out of $n$ studies and $\alpha$ the significance threshold. Corresponding to the study effect $\theta_i$, we can specify the power $1 - \beta_i$, the probability to be accepting a true result. Let $z_{\alpha,i}$ be the $1-\alpha$ quantile of a normal distribution with standard error $\hat{\se}_i$. The power of study $i$ can be estimated as:

\begin{align}
1 - \hat{\beta}_i &= F(z_\alpha) 
\end{align}
with $F$ being the cumulative normal distribution with mean $\hat{\theta}_M$ and standard deviation $\hat{\se}_i$. \\
If we assume no bias in $\theta_i$ and $\theta_M$, the expected number of significant study results is then just

\begin{align}
E &= \sum_{i = 1}^n (1 - \beta_i). \nonumber
\end{align}

@@

\begin{align}
\chi  &= \bigg( \frac{(O - E)^2}{E} + \frac{(O - E)^2}{n - E}\bigg) \nonumber
\end{align}
and consecutively, calculating a $p$\hspace{0.4mm}-value for the evidence against the null-hypothesis of $O = E$ with a $\chi^2$ distribution with one degree of freedom. Alternatively, one can also use a binomial test, which is encouraged when $n$ and $O$ is small. We will get a one sided $p$\hspace{0.4mm}~-value for excess significance, $\P(X \geq O)$, by computing

\begin{align}
p &= \sum_{i = O}^n\Big({n \choose i} p^i (1-p)^{n - i}\Big) \nonumber
\end{align}
with $p = E/n$ and $X$ being a binomial random variable with probability $p$.

@@

\begin{align}
\theta_i & = \beta_0 + \beta_1\sqrt{\se_i^2 + \tau^2} + \epsilon_i\sqrt{v_i + \tau^2}, \label{eq:limitmeta.regression} \\
\epsilon_i &\stackrel{\textrm{iid}}{\sim} N(0,1).
\end{align}

@@

\begin{align}
\mathbb{E}\big((\theta_i - \beta_0)/\sqrt{\se_i^2}\big) \rightarrow \beta_1 \textrm{ if } \se_i \rightarrow \infty \nonumber \\ %\label{limitmeta.infinitesample} \\
\mathbb{E}(\theta_i) \rightarrow \beta_0 + \beta_1 \tau \textrm{if} \se_i \rightarrow 0. \nonumber
\end{align}

@@

\begin{align}
\theta_i &\sim N(\mu_i, \sigma_i^2) &
\mu_i \sim N(\theta, \tau^2) \label{eq:population.model}
\end{align}
which is identical to the random-effects meta-analysis setting. $\theta$ is the population mean effect, $\sigma_i^2$ the within study variance and $\tau^2$ the between study variance. This is termed the \textit{population model}. \\
The \textit{selection model} is defined as follows. Suppose a selection of studies with reported %($\neq$ estimated) 
standard errors $\se$ (possibly different from $\sigma$). Only a proportion of the selection will be published, with the parameter $a$ defining the overall proportion of published studies and $b$ (assumed to be positive) defining how fast this proportion increases with $\se$ becoming smaller. Formally, the probability of selection given a reported standard error $\se$ is defined as
\begin{align}
P(\textrm{select}\given \se) &= \Phi(a + b/\se). \nonumber %\label{copas.selection1}
\end{align}

@@

\begin{align}
z = a + b/\se + \delta \nonumber %\label{copas.selection2}
\end{align}
with $\delta \sim N(0,1)$. $z$ is interpreted as the \textit{propensity for selection}. It is defined that the sign of $z$ must be positive in order for the study to be selected.
$a$ is some kind of global selection rate for each study and $b$ decides about the decline of selection probability with increasing $\se$.\\
So far, we have, for a study $i$
